The imprint of global magma oceans on exoplanet demographics

### 2023-01-30 src/tex/ms.tex
update PLATO figure with finer grid

    \begin{figure*}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            \textit{Left:} For a large planet yield of $N = \var{Nplato}$, even small planet fractions $\gtrsim \var{platoMinfrgh}$ allow a detection.
                A much smaller sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dashed green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            \textit{Right:} Evidences when only FGK or only M~dwarfs are considered.
                Only M~dwarfs host enough planets on both sides of the threshold instellation to allow a detection of the runaway greenhouse signal.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure*}

@@

For uncertainties in density measurements, we propagate normally distributed errors of mass measurements assuming $\sigma_\mathrm{M_\mathrm{P}} = \SI{10}{\percent}$, as expected for \plato.
As can be seen in Fig.~\ref{fig:plato_fgrid}, the detectability is enhanced when radius constraints can be augmented with mass measurements: At unchanged sample size, the difference in Bayesian evidence can be up to an order of magnitude larger.
Consequently, we achieve a statistically significant detection with smaller samples or lower fractions $f_\mathrm{rgh}$.
A density-based survey of 100 targets is roughly equivalent to a radius-based survey of 500 targets.
At $N=100$, pure radius measurements require $f_\mathrm{rgh} \gtrsim 0.5$ whereas bulk density measurements enable a detection from $f_\mathrm{rgh} \gtrsim 0.2$.

\subsubsection{Spectral type of target stars}\label{sec:results_FGK_M}
Since receiving radiation is sensitive on the spectral type of the host star, the share of planets on either side of $S_\mathrm{thresh}$ is different for FGK and M~dwarfs.
We tested the detectability of the runaway greenhouse signal when only FGK or only M~dwarfs are considered (see Fig.~\ref{fig:plato_fgrid}).
The samples are volume and magnitude-limited ($d_\mathrm{max} = \SI{55}{\parsec}, M_\mathrm{G} < 11$), which makes the M~dwarf sample significantly larger with \var{N_M} planets compared to \var{N_FGK} planets in the FGK sample.
No significant detection is possible in the pure FGK sample, independent of the assumed geophysical parameters.
In the M~dwarf sample, the evidence threshold is reached around $f_\mathrm{rgh} \sim 0.5$, similar to the case above where all spectral types are considered.

>>>>

    \begin{figure*}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected delta-evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            Median and $[16\mathrm{th}, 84\mathrm{th}]$ percentiles of randomized survey simulations are shown; $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            \textit{Left:} For a large planet yield of $N = \var{Nplato}$, even small planet fractions $\sim \var{platoMinfrgh}$ allow a detection.
                A sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dotted green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            \textit{Right:} Evidences when only FGK or only M~dwarfs are considered.
                Only M~dwarfs host enough planets on both sides of the threshold instellation to allow a reliable detection of the runaway greenhouse signal.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure*}

@@

For uncertainties in density measurements, we propagate normally distributed errors of mass measurements assuming $\sigma_\mathrm{M_\mathrm{P}} = \SI{10}{\percent}$, as expected for \plato.
As can be seen in Fig.~\ref{fig:plato_fgrid}, the detectability is enhanced when radius constraints can be augmented with mass measurements: At unchanged sample size, the difference in Bayesian evidence can be up to an order of magnitude larger.
Consequently, we achieve a statistically significant detection with smaller samples or lower fractions $f_\mathrm{rgh}$.
A density-based survey of 100 targets is roughly equivalent to a radius-based survey of 500 targets.
At $N=100$, pure radius measurements require $f_\mathrm{rgh} \gtrsim 0.4$ whereas bulk density measurements enable a detection from $f_\mathrm{rgh} \gtrsim 0.1$.

\subsubsection{Spectral type of target stars}\label{sec:results_FGK_M}
Since receiving radiation is sensitive on the spectral type of the host star, the share of planets on either side of $S_\mathrm{thresh}$ is different for FGK and M~dwarfs.
We tested the detectability of the runaway greenhouse signal when only FGK or only M~dwarfs are considered (see Fig.~\ref{fig:plato_fgrid}).
The samples are volume and magnitude-limited ($d_\mathrm{max} = \SI{55}{\parsec}, M_\mathrm{G} < 11$), which makes the M~dwarf sample significantly larger with \var{N_M} planets compared to \var{N_FGK} planets in the FGK sample.
No significant detection is possible in the pure FGK sample, independent of the assumed geophysical parameters.
In the M~dwarf sample, the evidence threshold is reached around $f_\mathrm{rgh} \sim 0.2$, similar to the case above where all spectral types are considered.
